[Re] Chaos in a long-term experiment with a plankton community

### 2016-02-17 article/article.tex
small edits

The reproduced results were qualitatively identical to those in the
original article, and therefore support the conclusion of chaotic
dynamics produced by non-linear species interactions. For example, all
Lyapunov exponents estimated by direct method were positive, as in the
original article, consistent with chaotic dynamics. Quantitative
differences may have resulted from difference in algorithms used. For
example,the original used the
\href{http://www.mpipks-dresden.mpg.de/~tisean/}{Tisean software} to
calculate Lyapunov exponents. As this was available from CRAN
\href{http://cran.r-project.org/web/packages/RTisean/index.html}{until
mid 2014} and since it is a bit less well integrated with R, we instead
use the tseriesChaos package \textcite{tseriesChaos}, which in any case
was largely inspired by the TISEAN project. In addition, there may have
been some difference in algorithm parameters, as not all parameters
required by the functions we used were reported in the original ms.

>>>>

The reproduced results were qualitatively identical to those in the
original article, and therefore support the conclusion of chaotic
dynamics produced by non-linear species interactions. For example, all
Lyapunov exponents estimated by direct method were positive, as in the
original article, consistent with chaotic dynamics. Quantitative
differences may have resulted from difference in algorithms used. For
example,the original used the
\href{http://www.mpipks-dresden.mpg.de/~tisean/}{Tisean software} to
calculate Lyapunov exponents. As this was available from CRAN
\href{http://cran.r-project.org/web/packages/RTisean/index.html}{until
mid 2014} and since it is a bit less well integrated with R, we instead
use the tseriesChaos package (\textcite{tseriesChaos}), which in any
case was largely inspired by the TISEAN project. In addition, there may
have been some difference in algorithm parameters, as not all parameters
required by the functions we used were reported in the original ms.
